Análisis descriptivo de datos - Socialización de la meritocracia

### 2021-03-26 production/prod_analisis.Rmd
renderizado
se agrega presentación a la pagina
tabla
tabla en paper

>>>>

save(basereg, file="../output/tables/basereg.RData")
save(mmn_td_cwc, file="../output/tables/mmn_td_cwc.R")
save(mml1_td_cwc1, file="../output/tables/mml1_td_cwc1.R")
save(mml1_td_cwc2, file="../output/tables/mml1_td_cwc2.R")
save(mml1_td_cwc3, file="../output/tables/mml1_td_cwc3.R")
save(mml1_td_cwc4, file="../output/tables/mml1_td_cwc4.R")
